Technical Report

### 2018-05-24 fully-abstract-comp/technical-report.tex
Downwards closure lemmas about the conditions on source configurations

\section{Proofs and lemmas}
\input{ftlr-proof-cases}

>>>>

\section{Lemmas}
\subsection{Well-behaved configurations}
\begin{lemma}
  \label{lem:check-stack-addr-before-call-dc}
For $n' \leq n$, if a configuration $\src{\Phi}$ is said to check $\stkb$ before calls in $\ta$ for $n$ steps, then $\src{\Phi'}$ is said to check $\stkb$ before calls in $\ta$ for $n'$ steps
\end{lemma}
\begin{proof}
  \lau{TODO}
\end{proof}

\begin{lemma}
  \label{lem:use-return-seals-call-dc}
  For $n' \leq n$, if a configuration $\src{\Phi}$ is said to use linker seals properly in $\ta$ with component parameters $\sigrets$, $\sigcloss$ for $n$ steps, then $\src{\Phi}$ is said to use linker seals properly in $\ta$ with component parameters $\sigrets$, $\sigcloss$ for $n'$ steps.
\end{lemma}
\begin{proof}
  \lau{TODO}
\end{proof}

\begin{lemma}
  \label{lem:handle-trusted-seals-prop-dc}
  For $n' \leq n$, if a configuration $\src{\Phi}$ is said to handle trusted seals properly in $\ta$ with component parameters $\sigrets$, $\sigcloss$ for $n$ steps, then $\src{\Phi}$ is said to handle trusted seals properly in $\ta$ with component parameters $\sigrets$, $\sigcloss$ for $n'$ steps.
\end{lemma}
\begin{proof}
  \lau{TODO}
\end{proof}

\begin{lemma}
  \label{lem:never-store-seal-code-cap-dc}
  For $n' \leq n$, if a configuration $\src{\Phi}$ is said to not store link seals and code capability in $\ta$ with component parameters $\sigrets$, $\sigcloss$ for $n$ steps, then $\src{\Phi}$ is said to not store link seals and code capability in $\ta$ with component parameters $\sigrets$, $\sigcloss$ for $n'$ steps.
\end{lemma}
\begin{proof}
  \lau{TODO}
\end{proof}

\section{Proofs}
\input{ftlr-proof-cases}
